Leadership across cultures and contexts: an exploratory analysis

### 2020-05-08 leadership_across_cultures_contexts.Rmd

Pawnee chiefs illustrate leadership involving several of the universal dimesions, including intelligence, conflict resolution, and generosity [@murrayXX]:

>>>>

Pawnee chiefs illustrate leadership involving several of the universal dimesions, including intelligence, conflict resolution, and generosity [@nq18-015]:
